Spoken Corpus of Karel Mako\v{n}

### 2018-04-09 2018-clarin-pisa/makon-data.tex
crap to delete for clarin 2018

I have focused on two major aspects of processing the material: 1. Making it
accessible to the public and 2. acquiring a complete transcription. The
% akustická úprava, indexy, vyhledávání

>>>>

I have focused on two major aspects of processing the material: 1. Making it
accessible to the public and 2. acquiring a complete transcription. To a lesser
extent, I have also worked towards 1. overcoming the acoustic difficulties for
listeners, 2. topically indexing some recordings and 3. enablind a full-text
search over the whole corpus.

\subsection{Access to the Corpus}

The speech recordings are available through two sources. First and foremost,
it is in the Clarin repository, which guarantees it will be easily available no
matter what fate this project will take.

Secondly, I have created a web application for listening to the recordings
directly in the browser. The web application is also capable of displaying the
transcription synchronously. When there is an error in the transcription (which
is frequently so in case of automatically acquired ones), the user can submit a
correction.

\subsection{Complete Transcription}

Transcription of the whole corpus has been the main focus for the majority of
the time spent on the project. The concept was to transcribe a few minutes from
scratch, train a HMM-based ASR model on that, evaluate the bulk of the corpus
and feed that to the web application, as a base for the users to correct.

We only have a single speaker, a restricted domain, relatively consistent
conditions, an extensive collection of the author's original books,
translations, comments and letters to build a well-fitting language model. So
even very little training data should give satisfactory results and the error
rate should drop rapidly as the training data would increase.

Well, the error rate did drop as the training data increased but the accuracy of
the speech recognition was more of a challenge than I had thought. Fot the most
part, the users were actually using the web interface to provide a new
transcription from scratch, ignoring the way too erroneous output of the ASR,
instead of merely correcting single errors, as was meant.

Still, the community managed to provide over 66 hours of high-quality manual
transcriptions, which have been used gradually as training data. Now, the
acoustically intact recordings are automatically transcribed well enough to
allow reading along and to do full-text search.

The word error rate on our test set is currently 42\% but it is probably lower
on clean recordings and also most mistakes are in word endings, so the meaning
is comprehensible. I am currently training a DNN acoustic model, so chances are
the ASR score will soon rise noticeably.

\subsection{Secondary Processing Attempts}

\subsubsection{Mitigating Acoustic Defects}

In a new version of the web interface (paper pending), I have implemented a
user-controllable parametric graphical equalizer. This can help significantly in
the case of narrow-band noise, which occurs on some recordings, predominantly in
the bass range.

This was a cheap solution for a low-hanging fruit but a more holistic approach
is
